Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-20 ms.tex
Committed tweak to final unfinished intro paragraph

% Convolutional and residual
In image space, \citep{petrillo_etal17} used data from the Kilo Degree
survey to train convolutional neural networks with the Kilo Degree
Survey. \citet{lanusse_etal17} using state-of-the-art residual
networks to work directly in the image space with minimal image
pre-processing.  A major strength of the \citet{lanusse_etal17}
implementation is that residual networks ..... , which regular
convolutional networks do not.

\todo{EDITING HERE: Double check that petrillo paper operates in image
  space, edit previous paragraph.}

>>>>

% Convolutional and residual
The most advanced use of neural networks for strong lensing
classification operate directly in image space.
\citep{petrillo_etal17} used mock Kilo Degree Survey data to train
convolutional neural networks, with a training set size of six million
images. \citet{lanusse_etal17} used state-of-the-art residual learning
to also work directly in the image space with minimal image
pre-processing.  A major strength of the \citet{lanusse_etal17}
implementation is that residual learning has been found to be easier
to train in deep neural networks, and can outperform implementations
of convolutional neural networks.
